Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
Added first draft of results section

@@

>>>>

The results of the study show some interesting results. The rejection of \textsubscript{0} Eff indicates that there is a difference between the efficiency of the inspection methods. This difference could be down to the

@@

\begin{table}
	\centering
	\begin{tabular}[Ht]{| l | l | l | l | l | l | l |}
	\hline
	 & A Faults & B Faults & C Faults & Mean & Median & Detection Rate\\
	\hline
	UC & 36 & 40 & 35 & 4.615384615 & 3.5 & 0.12 \\
	\hline
	CL & 31 & 47 & 28 & 5.48 & 5 & 0.14 \\
	\hline
	\end{tabular}
	\caption{Results Summary}
\end{table}

The results of the experiment appear to suggest that a check-list(CL) based review technique is more effective than a use-case(UC) based review technique. Given that the null hypothesis H\textsubscript{Eff} was rejected, it is a fair assumption to make. UC appears to find many more class A faults than CL, however, CL finds more class B faults and UC finds more class C faults. However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC. The slight variation in favour of the CL technique is further evidence that CL is more efficient and therefore more effective than UC.
